Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-14 paper/paper.tex
got rid of algpseudocode

\usepackage[utf8]{inputenc}
%\usepackage{xspace}
\usepackage{balance}
\usepackage{amsmath,amsfonts,mathtools,amsthm}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}

@@

\begin{algorithm}
    \renewcommand{\algorithmicrequire}{\textbf{Input:}}
    \renewcommand{\algorithmicensure}{\textbf{Output:}}
    \begin{algorithmic}[1]
        \Require 
        $k, \ell$,
        initial configuration $P_I$,
        sequence of  requests $\sigma_1, \dots, \sigma_N$ 
        \Ensure A final configuration $P_F$ 
        \State For each node $v$ create a singleton component $C_v$ and add it to $\mathcal{C}$
        \State{$P_0 := P_I$}
         \label{line:initcomponents}
        \For {each  request $\sigma_t=\{u,v\}, 1 \leq t \leq N$}
        \State Let $C_1 \ni u$ and $C_2 \ni v$ be the container components
        \If{$C_1 \neq C_2$}
        \State Unite the two components into a single component $C'$ and
        $\mathcal{C} = (\mathcal{C}\setminus\set{C_1, C_2}) \cup ~\set{C'}$ \label{line:mergecomponents}
%        \If{$\mathit{cluster}(C_1, P_{t-1}) \neq \mathit{cluster}(C_2, P_{t-1})$}
        \If{$\mathit{cluster}(C_1, P_{t-1}) \neq \mathit{cluster}(C_2, P_{t-1})$}
        \Comment{if not in the same cluster}
        \State $P_{t} = \mathit{re\mhyphen partition}(P_{t-1}, P_I, \mathcal{C}$) \label{line:rebalance} 
        \Comment{move to $P$ closest to $P_I$}
        \EndIf
        \EndIf
        \EndFor
    \end{algorithmic}
    \caption{Perfect Partition Learner (PPL)}
    \label{alg:ppl}
      \end{algorithm}

>>>>

\usepackage[utf8]{inputenc}
%\usepackage{xspace}
\usepackage{balance}
\usepackage{amsmath,amsfonts,mathtools,amsthm}
\usepackage{algorithmic}
\usepackage{algorithm}

@@

\begin{algorithm}
    \renewcommand{\algorithmicrequire}{\textbf{Input:}}
    \renewcommand{\algorithmicensure}{\textbf{Output:}}
    \begin{algorithmic}
%        \Require 
%        $k, \ell$,
%        initial configuration $P_I$,
%        sequence of  requests $\sigma_1, \dots, \sigma_N$ 
%        \Ensure A final configuration $P_F$ 
        \STATE {For each node $v$ create a singleton component $C_v$ and add it to $\mathcal{C}$}
        \STATE{$P_0 := P_I$}
         \label{line:initcomponents}
        \FOR {each  request $\sigma_t=\{u,v\}, 1 \leq t \leq N$}
        \STATE Let $C_1 \ni u$ and $C_2 \ni v$ be the container components
        \IF{$C_1 \neq C_2$}
        \STATE {Unite the two components into a single component $C'$ and
        $\mathcal{C} = (\mathcal{C}\setminus\set{C_1, C_2}) \cup ~\set{C'}$} \label{line:mergecomponents}
        \IF{$\mathit{cluster}(C_1, P_{t-1}) \neq \mathit{cluster}(C_2, P_{t-1})$
	     \COMMENT{i.e.~if not in the same cluster}    
    	}       
        \STATE {$P_{t} = \mathit{re\mhyphen partition}(P_{t-1}, P_I, \mathcal{C})$} 
         \COMMENT{move to $P$ closest to $P_I$}
        \label{line:rebalance} 
        \ENDIF
        \ENDIF
        \ENDFOR
    \end{algorithmic}
    \caption{Perfect Partition Learner (PPL)}
    \label{alg:ppl}
      \end{algorithm}
